A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-24 paper/prab.tex
spelling out Figure when at beginning of sent.
making equation span two columns
linda's second round of edits
remove SwissFEL ties

\documentclass[%
reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

@@

\usepackage{graphicx,xcolor,enumitem}
\newcommand{\lsnote}[1]{\textsf{{\color{violet}{ LS note:}   #1 }}}

@@

\newcommand{\nrnote}[1]{\textsf{{\color{violet}{ NN note:}   #1 }}}

\begin{document}

@@

\author{Y. Ineichen }
\affiliation{% 
	place holder 1
}%

\author{A. Adelmann}
\email{andreas.adelmann@psi.ch}
\author{A. Kolano}
\altaffiliation[Also at ]{
	University of Huddersfield, West Yorkshire, United Kingdom and  CERN, Genf}
\author{C. Metzger-Kraus}
\altaffiliation[Also at ]{AiF Projekt GmbH}
\affiliation{
	PSI, Villigen, Switzerland}%

@@

Here, we will focus on a real world applications arising from Paul Scherrer Institut's (PSI)
  \textsc{SwissFEL}~\cite{pedr:10} activities, and a high charge photoinjector 
  at the Argonne Wakefield Accelerator (AWA). Both of which have an immediate and a
  long-range impact, by optimizing important parameters for rf photoinjectors.

@@

Applied to multi-objective optimization problems, genes correspond to
  design variables.
The fitness of an individual is loosely related to the value of the objective
  functions for the corresponding genes.
Fig.~\ref{fig:varsel} schematically depicts the connection of the
  components introduced above.
The process starts with an initially random population of individuals, each
  individual with a unique set of genes and corresponding fitness,
  representing one location in the search space.
In a next step the population is processed by the selector
  determining the $k$ fittest individuals according to their fitness values.
While the $k$ fittest individuals are passed to the variator, the
  remaining $n-k$ individuals are eliminated from the population.
The \textsc{Variator} mates and recombines the $k$ fittest individuals to
  generate new offspring.
After evaluating the fitness of all the freshly born individuals a
  \textit{generation} cycle has completed and the process can start anew.

@@

\begin{flushleft}
\begin{align} \label{eqn:bench}
\text{min} & \left[ 1 - \exp \left( -1 \left(
\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
& \left. 1 - \exp \left( -1 \left(
\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
\text{.}
\end{align}
\end{flushleft}

@@

\input{theor-experiment} %periment}

@@

The authors thank the \textsc{SwissFEL} and AWA teams for contributing to the
  formulation of optimization problems. 
  We gratefully acknowledge the computing resources provided on Bebop,
  a HPC cluster operated by the LCRC at ANL.
  Thanks to Scott Doran for providing CAD drawings of the AWA beam lines.
  This work was partly supported by the 
  U.S. Department of Energy, Office of Science, under 
  contract number DE-AC02-06CH11357 and grant number DE-SC0015479.

>>>>

\documentclass[%
reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
%rmp,
prstab,
%prstper,
%floatfix,
]{revtex4-1}

@@

\usepackage{graphicx,xcolor,enumitem}
%\usepackage{cuted}
\newcommand{\lsnote}[1]{\textsf{{\color{violet}{ LS note:}   #1 }}}

@@

\newcommand{\nrnote}[1]{\textsf{{\color{blue}{ NN note:}   #1 }}}
\newcommand{\lsedit}[1]{\textsf{{\color{violet}{ ls note:}   #1 }}}
\begin{document}

@@

\author{A. Adelmann}
\email{andreas.adelmann@psi.ch}
\author{Y. Ineichen }
%\email{yves.ineichen@gmail.com}
\author{A. Kolano}
\altaffiliation[Also at ]{
	University of Huddersfield, West Yorkshire, United Kingdom and  CERN, Genf}
\author{C. Metzger-Kraus}
\affiliation{
	PSI, Villigen, Switzerland}%

@@

Here, we will focus on a real world application, the a high charge photoinjector 
  at the Argonne Wakefield Accelerator (AWA).

  %Both of which have an immediate and a
  %long-range impact, by optimizing important parameters for rf photoinjectors.

@@

Applied to multi-objective optimization problems, genes correspond to
  design variables.
The fitness of an individual is loosely related to the value of the objective
  functions for the corresponding genes.
Figure~\ref{fig:varsel} schematically depicts the connection of the
  components introduced above.
The process starts with an initially random population of individuals, each
  individual with a unique set of genes and corresponding fitness,
  representing one location in the search space.
In a next step the population is processed by the selector
  determining the $k$ fittest individuals according to their fitness values.
While the $k$ fittest individuals are passed to the variator, the
  remaining $n-k$ individuals are eliminated from the population.
The \textsc{Variator} mates and recombines the $k$ fittest individuals to
  generate new offspring.
After evaluating the fitness of all the freshly born individuals a
  \textit{generation} cycle has completed and the process can start anew.

@@

%\begin{strip}
	\begin{widetext}
		\begin{align} \label{eqn:bench}
		\text{min} & \left[ 1 - \exp \left( -1 \left(
		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
		\vspace{3em} 
		& \left. 1 - \exp \left( -1 \left(
		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
		\vspace{3em} \\
		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
		\text{.}
		\end{align}
	\end{widetext}
%\end{strip}

@@

\input{theor-experiment}

@@

The authors thank the AWA team for contributing to the
  formulation of optimization problems. 
  We gratefully acknowledge the computing resources provided on Bebop,
  a HPC cluster operated by the LCRC at ANL.
  Thanks to Scott Doran for providing CAD drawings of the AWA beam lines.
  This work was partly supported by the 
  U.S. Department of Energy, Office of Science, under 
  contract number DE-AC02-06CH11357 and grant number DE-SC0015479.
